### 2021-04-24 submission/manuscript.Rmd
Fig 5 caption edits

\includegraphics{figure_5.pdf}
A. Experimental timeline for groups receiving PEG treatment post clindamycin gavage. B. Median and individual CFU/g of C. difficile measured over time via culture. Asterisks indicate time points with significant differences between groups using Kruskall-Wallis tests with a Benjamini-Hochberg correction. Limit of detection is 1e2 CFU/g. Background shading indicates PEG treatment period for applicable groups. Opacity of points reflects time point. C. Median and individual Shannon Diversity measured over time. Asterisks, background shading, and opacity of points consistent with (B). D. Median and individual richness measured over time. Asterisks, background shading, and opacity of points consistent with (B).

>>>>

``` {r figure_5_permanova}
fig_5_permanova_results = read_tsv("data/process/post_CDI_PEG_permanova_stools.tsv")
r_sq_ordered_perm = permanova_results %>% arrange(desc(R2)) %>% 
  select(`effects`, `R2`, `Pr(>F)`) %>%
  filter(`Pr(>F)` < .05) #filter for sig
fig_5_permanova_sig_P_val <- r_sq_ordered_perm[,3] %>% sum()
fig_5_permanova_sig_R2 <- r_sq_ordered_perm[,2] %>% sum() #0.9280951 
```

\includegraphics{figure_5.pdf}
A. Setup of experimental timeline for groups receiving PEG treatment post clindamycin gavage. All mice were administered 10 mg/kg clindamycin intraperitoneally (IP) 1 day before challenge with C. difﬁcile 630 spores on day 0. 15% PEG 3350 was administered in the drinking water for 1 day. Mice feces were collected daily through the end of the experiment (30 days post-infection for Clind. + 1-day PEG group, 15 days post-infection for all others). CFU quantification data was not available for each mouse due to stool sampling difficulties (particularly the day the mice came off of the PEG treatment) or early deaths. B. CFU/g of C. difficile stool measured over time via serial dilutions. C. Median and individual Shannon Diversity measured over time. D. Median and individual richness measured over time. B-D. Asterisks indicate time points with significant differences between groups using Kruskall-Wallis tests with a Benjamini-Hochberg correction for testing multiple times points. Black line represents the limit of detection for the first serial dilution. Background shading indicates PEG treatment period for applicable groups. Opacity of points reflects time point. The data presented are from a total of *** separate experiments.
